Plots

### 2023-10-12 Code/Plots.Rmd
Fixed typo on axix

venue_effects_with2022<- ggplot(venues, aes(x=year, y = condval)) + geom_point() + 
  labs(x = "Year", y = "Year Effect") +
  scale_x_continuous(limits = c(1998,2024), breaks = seq(1999, 2024, 2)) +
  scale_y_continuous(limits = c(-0.1, 0.1))
```

@@

venue_effects_without2022 <- ggplot(venues, aes(x=year, y = condval)) +
  geom_point() + 
  labs(x = "Year", y = "Year Effect") +
  scale_x_continuous(limits = c(1998,2024), breaks = seq(1999, 2024, 2)) +
  scale_y_continuous(limits = c(-0.1, 0.1))
```

>>>>

venue_effects_with2022<- ggplot(venues, aes(x=year, y = condval)) + geom_point() + 
  labs(x = "Venue", y = "Venue Effect") +
  scale_x_continuous(limits = c(1998,2024), breaks = seq(1999, 2024, 2)) +
  scale_y_continuous(limits = c(-0.1, 0.1))
```

@@

venue_effects_without2022 <- ggplot(venues, aes(x=year, y = condval)) +
  geom_point() + 
  labs(x = "Venue", y = "Venue Effect") +
  scale_x_continuous(limits = c(1998,2024), breaks = seq(1999, 2024, 2)) +
  scale_y_continuous(limits = c(-0.1, 0.1))
```
